Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-11-23 jss/article.tex
jss update

\section[Introduction]{Introduction}
Biological pathways and networks comprise sets of interactions or functional
relationships, occurring at the molecular level in living cells

>>>>

\section[Introduction]{Introduction}
Biological pathways and networks comprise sets of interactions or functional
relationships, occurring at the molecular level in living cells
\citep{adriaens2008public}.  A large body of knowledge on cellular biochemistry
is organized in publicly available repositories such as the KEGG database
\citep{kanehisa2011kegg}, Reactome \citep{croft2014reactome} and MINT
\citep{zanzoni2002mint}. All these biological databases facilitate a large
spectrum of analyses, improving our understanding of cellular systems. For
instance, it is a very common practice to cross the output of high-throughput
experiments, such as mRNA or protein expression levels, with curated biological
pathways in order to visualize changes, analyze their impact on a network and
formulate new hypotheses about biological processes. Many biologists and
computational biologists establish list of genes of interest (e.g. a list of
genes that are differentially expressed between two conditions, such as normal
vs disease) and then try to see if known biological pathways are enriched with
this list of genes.

We have recently released the Atlas of Cancer Signalling Network (ACSN), a
web-based database which
describes signaling and regulatory molecular processes that occur in
a healthy mammalian cell but that are frequently deregulated during
cancerogenesis. ACSN is
